---
title: "Statistical Analysis Report"
author: "Xinyi Xie B00812989 Yixuan Wang B00815205 Yingwei Guo B00736113 Wenhui Wang B00843110"
date: "12/11/2020"
output:
  html_document:
   toc: true
   toc_float: true
   toc_depth: 6
   collapsed: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(GGally)
require(olsrr)

dat <- read_csv("Nutrition__Physical_Activity__and_Obesity_-_Behavioral_Risk_Factor_Surveillance_System.csv", col_names = TRUE)

dat$LocationAbbr <- NULL
dat$YearEnd <- NULL
dat$Low_Confidence_Limit <- NULL
dat$High_Confidence_Limit <- NULL
dat$Datasource <- NULL
dat$Data_Value_Unit <- NULL
dat$Data_Value_Type <- NULL
dat$Data_Value_Alt <- NULL
dat$Data_Value_Footnote_Symbol <- NULL
dat$Data_Value_Footnote <- NULL
dat$Total <- NULL
dat$GeoLocation <- NULL
dat$ClassID <- NULL
dat$TopicID <- NULL
dat$DataValueTypeID <- NULL
dat$StratificationCategoryId1 <- NULL
dat$StratificationID1 <- NULL
# dat <- dat %>% filter(Question %in% c("Percent of adults aged 18 years and older who have obesity", "Percent of adults aged 18 years and older who have an overweight classification"))
dat <- dat[dat$Stratification1 != "Total" & dat$YearStart == 2014, ]
age <- dat %>% filter(Stratification1 %in% c("18 - 24", "25 - 34", "35 - 44", "45 - 54", "55 - 64", "65 or older"))
age[973:1296, ] <- age[1:324, ]
gender <- dat %>% filter(Stratification1 %in% c("Male", "Female"))
gender <- rbind.data.frame(gender, gender, gender, gender)
edu <- dat %>% filter(Stratification1 %in% c("Less than high school", "High school graduate", "Some college or technical school", "College graduate"))
edu <- rbind.data.frame(edu, edu)
inc <- dat %>% filter(dat$Stratification1 %in% c("Less than $15,000", "$15,000 - $24,999","$25,000 - $34,999","$35,000 - $49,999", "$50,000 - $74,999","$75,000 or greater", "Data not reported"))
inc[1135:1296, ] <- inc[1:162, ]
race <- dat %>% filter(Stratification1 %in% c("Non-Hispanic White", "Non-Hispanic Black","Hispanic", "Asian", "Hawaiian/Pacific Islander","American Indian/Alaska Native","2 or more races", "Other"))

newd <- cbind.data.frame(age$QuestionID, age$Data_Value, gender$Stratification1, edu$Stratification1, inc$Stratification1, race$Stratification1)
names(newd) <- c("QuestionID", "Proportion", "Gender", "Education", "Income", "Race")
```

## 1.Abstract

To better understanding the association between physical activity and obesity, the data was collected among the 55 states and districts in the US from the year of 2011 to the year of 2016. Here we only focused on the year of 2014 since it has the largest observations. And we focused question Q036, Q037 and Q047 to find out the association between physical activity and obesity.



## 2.Introduction

Data was collected based on behaviroal risk factor (physical activity and obesity) among the 55 states and districts in the US from 2011 to 2016. Questsions were asked among the 55 districts as follows:

  - Q036:Percent of adults aged 18 years and older who have obesity;
  - Q037:Percent of adults aged 18 years and older who have an overweight classification;
  - Q018:Percent of adults who report consuming fruit less than one time daily;
  - Q019:Percent of adults who report consuming vegetables less than one time daily;
  - Q046:Percent of adults who engage in muscle-strengthening activities on 2 or more days a week;
  - Q043:Percent of adults who achieve at least 150 minutes a week of moderate-intensity aerobic physical activity or 75 minutes a week of vigorous-intensity aerobic activity (or an equivalent combination);
  - Q044:Percent of adults who achieve at least 150 minutes a week of moderate-intensity aerobic physical activity or 75 minutes a week of vigorous-intensity aerobic physical activity and engage in muscle-strengthening activities on 2 or more days a week;
  - Q045:Percent of adults who achieve at least 300 minutes a week of moderate-intensity aerobic physical activity or 150 minutes a week of vigorous-intensity aerobic activity (or an equivalent combination);
  - Q047:Percent of adults who engage in no leisure-time physical activity.
  
For each question, the proportion and corresponding confidence limit were provided. Additionally, sample size, age, education background, gender, income and race were also given. 
<!-- Since we are interested in obesity and overweight percent, we only focus on the first 2 questions here.  -->


## 3.Data Description
Introduce new data point

```{r}
dat1=rbind(dat,rep(1,33))
```

### 3.1 Gender

```{r, fig.width=12}
ggplot(data=newd, aes(x=Gender,y=Proportion, fill = QuestionID)) +
  geom_boxplot(width = 0.4) +
  facet_wrap(~QuestionID)
```
From what is shown in the figure above, it can be seen that the difference in gender causes changes in the data. As in Q036, male have a greater influence on the percentage of obese adults over 18 years old. However, in Q037 and Q048, female have a higher propotion of data.

### 3.2 Education

```{r, fig.width=12}
ggplot(data=newd, aes(x=Education,y=Proportion, fill = QuestionID)) +
  geom_boxplot(width = 0.4) +
  facet_wrap(~QuestionID) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
From boxplot above, we could find that difference between 3 groups of different education levels and all three groups contain outliers. For example, in group Q036, proportion of adults who have obesities in level of less than high school is much higher than others; but medians of 4 levels are similar. In Q037, mean of 4 levels are higher than group Q036 and Q047.

### 3.3 Income

```{r, fig.width=12}
ggplot(data=newd, aes(x=Income,y=Proportion, fill = QuestionID)) +
  geom_boxplot(width = 0.4) +
  facet_wrap(~QuestionID) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
In the boxplot above, we can figure out the difference income level clearly. For example, group Q047 have lowest income compared to other two groups.

### 3.4 Race

```{r, fig.width=12}
ggplot(data=newd, aes(x=Race,y=Proportion, fill = QuestionID)) +
  geom_boxplot(width = 0.4) +
  facet_wrap(~QuestionID) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
From the above figure, we can see differences between diffident races. For example, in Q037, when the proportion of American Indian/Alaska Native’s and Non-Hispanic’s level are medium, they have the highest proportion of overweight in adults compared with other groups. In Q047, adults in Hawaiian/Pacific Islander has the lowest rate of obesity among those who do not exercise in leisure- time.


## 4.Method


### 4.1.1 Model

```{r}
m <- lm(Proportion ~., data= newd)
ols_step_all_possible(m)
```
Since we have five variables, we have 31 combinations of models. The above is the arrangement of the five variables. Among them, index1-5 is a model controlled by a single variable; 6-15 are two variables; 16-25 are three variables; 26-30 are four variables; 31 is a model controlled by five variables.

### 4.1.2 Model Plot

```{r}
plot(ols_step_all_possible(m))
```
In general, the larger R-Squared means the better model's fitting effect. However, as the number of variables increases, R-Squared will inevitably increase, so it is impossible to truly quantify the degree of accuracy, but only roughly quantify. Therefore, we use the adjusted coefficient of determination, which is the adjusted fitting coefficient, to remove the increase in the R-squared effect of the increase in explanatory variables, so the largest value is the best in Adj.R-square,so 6, 16, 26, 31 are better. C(p) values as small as possible, so 7, 20, 29 are better. AIC and BIC are used to measure model fit and model size, so we give preference to models with smaller values of AIC and SBC with 6 and 16. In summary, 6 and 16 are relatively good, but they cannot be used as the final result. We have to refer to the result obtained by backward.

### 4.2 Best Subset Regression

```{r}
ols_step_best_subset(m)
```

```{r}
plot(ols_step_best_subset(m))
```

Through further analysis, we found that more variables are not response the better model. This can be seen by the figure of Adj.R-squared. Therefore, Model 3 is more appropriate. The smaller value of C(p), the more suitable of the model, so 3, 4, and 5 are more suitable. Model 3 is the most smallest value in the AIC figure, so it is the best. In SBC, model 2 and model 3 are more suitable. The abscissa of the line chart represents the number of variables in the model, so it is more appropriate for the model to contain 3 variables.

### 4.3 Backward

```{r}
ols_step_backward_p(m)
plot(ols_step_backward_p(m))
```
The backward method is to obtain suitable variables by gradually deleting the predictor variables. This method based on the P-value and build a regression model from a set of predefined variables until there are no remaining variables to delete. We assume that all five predictors exist in the model.Through screening, we deleted Income and Race. The final model only contains QuestionID, Gender and Education, the specific analysis is shown in the figure below.

## 5.Result

### 5.1 Final Model

```{r}
m <- lm(Proportion ~ QuestionID + Gender + Education, data= newd)
summary(m)
plot(m)
```

Based on the above analysis, we can see that the proportion of adults aged 18 years and older who have obesity, percent of adults aged 18 years and older who have an overweight classification and percent of adults who engage in no leisure-time physical activity are significantly associated with gender and education status (p-value < 0.05).

Compared with Percent of adults aged 18 years and older who have an overweight classification, the Percent of adults aged 18 years and older who have an overweight classification is 6.24-unit higher and the Percent of adults who report consuming fruit less than one time daily is 5.73-unit lower. Compared with Female, the proportion of male is around 1-unit higher. And for the higher education status participants, the lower proportion of the obesity will be. 

## 6.Conclusion

The obesity is significantly associated with gender and education status at the significance level of 5%. Compared with Female, the male had higher change of getting obesity. And the higher education level is, the lower chance of getting obesity. 

## 7.Appendix

[Data source for the nutrition data](https://www.kaggle.com/spittman1248/cdc-data-nutrition-physical-activity-obesity)

[R Markdown file](https://github.com/Dal-stat-3340-final-project-group-9/Final-Project/blob/main/Final%20Project%20Group9.Rmd)
